Software Citation Principles

### 2016-03-21 sc-principles/software-citation-principles.tex
Updates from ShareLaTeX

There are many reasons why this lack of both software citations in general and
standard practices for software citation are of concern:

@@

With close to 50 working group participants (\ref{app:wg_members}) representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants, with the life sciences, astrophysics, and geosciences being particularly well-represented in the submitted
resources.

@@

Some of the most actionable work has come from the Software Sustainability Institute (SSI) in the form of blog posts written by their community fellows:

@@

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors and as noted in the introduction (\S\ref{sec:intro}), there is evidence that authors follow instructions if they exist ~\cite{10.1371/journal.pone.0136631}.

In a later post on the SSI blog, Jackson gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries~\cite{ssi-how-shalt-i-cite-thee},
and Knepley et al.\ do similarly~\cite{knepley2013accurately}.

>>>>

There are many reasons why this lack of both software citations in general and
standard practices for software citation are of concern: \katznote{Are there any more
items that should be added to this list?}

@@

With close to 50 working group participants representing a range of research domains, the working group was tasked to
document existing practices in their respective communities. A total of 47 documents were submitted by working group
participants, with the life sciences, astrophysics, and geosciences being particularly well-represented in the submitted
resources.

\textbf{Summary of submitted resources}

\asnote{Should mention that a number of communities have already focussed their attention on issues around data citation and while
this isn't exactly the same there are many similarities (what is different exactly?).}

@@

Some of the most actionable work has come from the NSF Software Infrastructure for Sustained Innovation (SSI) program in the form of blog posts written by their community fellows:

@@

Wilson suggests that software authors include a `CITATION' file that documents exactly how the
authors of the software would like to be cited by others~\cite{ssi-citation-files}. While this isn't a formal metadata specification (it's not machine
readable for example) this does offer a solution for authors wishing to give explicit instructions to potential citing authors.\dmnote{There is evidence from databases that people actually tend to follow such instructions if they exist: \cite{10.1371/journal.pone.0136631}.} \katznote{added this ref to the introduction - not sure if it is still needed here too}
In a later post on the SSI blog, Jackson gives a good overview of some of the approaches
package authors have taken to automate the generation of citation entities such as bibtex entries~\cite{ssi-how-shalt-i-cite-thee},
and Knepley et al.\ do similarly~\cite{knepley2013accurately}.
